### 2016-12-13 poster/poster.tex
trying to write some conclusion-y things
add dynet numbers
clean up time breakdown

As expected for neural networks, most of the runtime is spent in
matrix multiplication. Focusing on the most frequent function call
(a variant of \texttt{magma\_lds128\_sgemm\_kernel}):

@@

\begin{tabularx}{\textwidth}{l|r}
\textbf{Framework}  & \textbf{Percent time spent in top \texttt{magma\_lds128...}} \\  \hline
TensorFlow  &  68.87\% \\
Theano  & 49.90\% \\
DyNet   & ... \\
\end{tabularx}

@@

\begin{tabularx}{\textwidth}{c|lll}
Metric 										& Dynet & TensorFlow & Theano \\ \hline
\texttt{\detokenize{achieved_occupancy}}			&		.	&		0.062			&		0.062		\\
\texttt{\detokenize{sm_efficiency}}					&		.	&		22.58\%			&		16.04\%		\\
\texttt{\detokenize{warp_efficiency}}					&		.	&		100.0\%			&		99.99\%		\\
\texttt{\detokenize{warp_nonpred_efficiency}}	&		.	&		99.95\%			&		99.91\%		\\
\texttt{\detokenize{global_hit_rate}}					&		.	&		0.00\%			&		0.00\%		\\
\texttt{\detokenize{local_hit_rate}}					&		.	&		0.00\%			&		0.00\%		\\
\texttt{\detokenize{dram_read_throughput}}*		&		.	&		11.07			&		9.97		\\
\texttt{\detokenize{dram_write_throughput}}**		&		.	&		411.99			&		503.54		\\
\end{tabularx}

@@

>>>>

As expected for neural networks, most of the runtime is spent in
matrix multiplication. In every framework, one of the most used function calls is
a variant of \texttt{magma\_lds128\_sgemm\_kernel}, used for matrix multiplication.

@@

\textbf{Time spent in various functions}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

\begin{tabularx}{\textwidth}{c|lll}
\centering\textbf{Framework} & Dynet &  TensorFlow & Theano \\  \hline
\specialcell{matrix multiply \\(\texttt{magma\_lds128...})} & 29.64\%  &  68.87\% & 49.90\% \\
CUDA memset & 40.13\% & 0.00\% & 0.24\% \\
\end{tabularx}

@@

\begin{tabularx}{\textwidth}{c|lll}
Metric 										& Dynet & TensorFlow & Theano \\ \hline
\texttt{\detokenize{achieved_occupancy}}			&		0.062	&		0.062	&		0.062		\\
\texttt{\detokenize{sm_efficiency}}					&		16.64\%	&		22.58\%	&		16.04\%		\\
\texttt{\detokenize{warp_efficiency}}					&		100.0\%	&		100.0\%	&		99.99\%		\\
\texttt{\detokenize{warp_nonpred_efficiency}}	&		100.0\%	&		99.95\%	&		99.91\%		\\
\texttt{\detokenize{global_hit_rate}}					&		2.88\%	&		0.00\%	&		0.00\%		\\
\texttt{\detokenize{local_hit_rate}}					&		0.00\%	&		0.00\%	&		0.00\%		\\
\texttt{\detokenize{dram_read_throughput}}*		&		10.07	&		11.07	 	&		9.97 	\\
\texttt{\detokenize{dram_write_throughput}}**	&		357.63&		411.99 &		503.54	\\
\end{tabularx}

@@

Many tradeoffs to consider when selecting a framework: none of them
win across the board.
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
    \item Performance: see above!
    \item Simple or complicated installation?
    \item Is it well-documented?
    \item Is there a steep learning curve?
    \item Are there convenient built-ins?
    \item How difficult is it to debug computation graphs?
\end{itemize}
}
